---
title: "ReMis_Main_processed_Analysed"
author: "Marton Kovacs"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: html_document
---

# Load packages

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(readxl)
library(qdap)
library(papaja)
library(patchwork)
library(skimr)
library(viridis)
library(ggthemes)
library(ggrepel)
```

# Load functions

```{r}
source("utils.R")
```

# Relationship between mistake types by mistake causes
## Read in processed data

```{r}
cause_type_relationship <- read_tsv( "Data/Processed/ReMis_Main_Processed_Cause_Type_Relationship_Analysis_data.tsv")
```

## Data descriptives

```{r}
skim(cause_type_relationship) %>% summary()

skim(cause_type_relationship)
```

## Data transformation

For the plot we are recoding the different cause groups to match APA 6th format.

```{r}
cause_type_relationship <- 
  cause_type_relationship %>% 
  mutate(group_cause_meta = case_when(group_cause == "lack of knowledge/experience" ~ "Lack of knowledge",
                                      group_cause == "bad or lack of planning" ~ "Bad project preparation or management",
                                      group_cause == "bad or lack of standards" ~ "Bad project preparation or management",
                                      group_cause == "bad skill management" ~ "Bad project preparation or management",
                                      group_cause == "miscommunication" ~ "Bad project preparation or management",
                                      group_cause == "project management issue" ~ "Bad project preparation or management",
                                      group_cause == "time management issue" ~ "Bad project preparation or management",
                                      group_cause == "risking human error" ~ "Bad project preparation or management",
                                      group_cause == "technical issue" ~ "External difficulties",
                                      group_cause == "too high complexity" ~ "External difficulties",
                                      group_cause == "inattention" ~ "Personal difficulties",
                                      group_cause == "carelessness" ~ "Personal difficulties",
                                      group_cause == "overconfidence" ~ "Personal difficulties",
                                      group_cause == "physical and mental constraints" ~ "Personal difficulties",
                                      group_cause == "lack of control" ~ "Personal difficulties"))
```

Counting how many respondents listed a specific cause for each mistake type.

```{r}
con_tab <- as_tibble(xtabs(~ group_type + group_cause_meta, data = cause_type_relationship))
```

Calculating the percentages for each count.

```{r}
relationship_plot_data <- 
  con_tab %>% 
  group_by(group_type) %>% 
  mutate(n_sum = sum(n)) %>% 
  ungroup() %>%
  mutate(prop = round(n / n_sum * 100)) %>%
  filter(n_sum >= 10)
```

Creating labels for the plots' Y axis with the different mistake types and their count in this analysis.

```{r}
relationship_plot_label <- 
  relationship_plot_data %>% 
  mutate(label = paste0(group_type, " (", n_sum, ")"))
```


```{r}
# Plot with the label of the most frequent cause
relationship_plot_data %>% 
    ggplot(aes(x = reorder(group_type, n), y = n)) +
    geom_bar(stat = "identity") +
    geom_text(data = relationship_plot_label, aes(y = n_sum, label = label),
              hjust = -0.1, size = 3,
              position = position_dodge(width = 1),
              inherit.aes = TRUE) +
    scale_y_continuous(expand = c(0,0), limit = c(0, 65)) +
    coord_flip() +
    labs(x = "Data Management Mistake Types",
         y = "Count") +
    theme(axis.text.x = element_text(),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          axis.ticks = element_line(),
          axis.line = element_line())

# Stacked barplot of all the causes
relationship_plot_data %>% 
    ggplot(aes(x = reorder(group_type, n), y = n, group = n, fill = group_cause_meta)) +
    geom_bar(stat = "identity") +
    scale_fill_colorblind() +
    scale_y_continuous(expand = c(0,0), limit = c(0, 65)) +
    coord_flip() +
    labs(x = "Data Management Mistake Types",
         y = "Count") +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          axis.ticks = element_line(),
          axis.line = element_line(),
          axis.title = element_text(size = 20),
          legend.title = element_blank(),
          legend.position = c(0.75, 0.4),
          legend.text = element_text(size = 15))

ggsave("Figures/cause_type_relationship_all_stacked.png", width = 14.4, height = 8, plot = last_plot())
```

# Relationship between mistake types and mistake outcomes
# Read in processed data
```{r}
outcome_type_relationship <- read_tsv( "Processed/ReMis_Main_Processed_Outcome_Type_Relationship_Analysis_data.tsv")
```

# Data descriptives
```{r}
skim(outcome_type_relationship) %>% summary()

skim(outcome_type_relationship)
```

# Relationship between causes and types together for the most serious and recurring mistakes
```{r}
con_tab <- as_tibble(xtabs(~ group_type + group_outcome, data = outcome_type_relationship))

relationship_plot_data <- con_tab %>% 
  group_by(group_type) %>% 
  mutate(n_sum = sum(n)) %>% 
  ungroup() %>%
  mutate(prop = round(n / n_sum * 100)) %>%
  filter(n_sum >= 10) %>% 
  mutate(group_outcome = case_when(group_outcome == "financial lost" ~ "financial loss",
                                   TRUE ~ group_outcome))

relationship_plot_label <- relationship_plot_data %>% 
  group_by(group_type) %>% 
  mutate(highest_prop = case_when(prop == max(prop) ~ 1L,
                                  TRUE ~ 0L)) %>% 
  filter(highest_prop == 1) %>% 
  mutate(label = paste(group_outcome, prop, "%"),
         label = paste(label, collapse = " and\n "))

# Stacked barplot
relationship_plot_data %>% 
    ggplot(aes(x = reorder(group_type, n), y = n, group = n, fill = group_outcome)) +
    geom_bar(stat = "identity") +
    scale_fill_colorblind() +
    scale_y_continuous(expand = c(0,0)) +
    coord_flip() +
    labs(x = "Data Management Mistake Types",
         y = "Count") +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          panel.background = element_blank(),
          panel.grid = element_blank(),
          axis.ticks = element_line(),
          axis.line = element_line(),
          axis.title = element_text(size = 20),
          legend.title = element_blank(),
          legend.position = c(0.75, 0.4),
          legend.text = element_text(size = 15))

ggsave("Figures/outcome_type_relationship_all_stacked.png", width = 14.4, height = 8, plot = last_plot())
```

# Descriptives of the sample

# Read in data

```{r}
descriptives <- read_tsv("Processed/ReMis_Main_Processed_Descriptive_data.tsv")
```

# The number of distinct respondents

```{r}
descriptives %>% 
  distinct(response_id) %>% 
  count()
```

# Data descriptives

```{r}
skim(descriptives)
```

# Years in field descriptives

```{r}
descriptives %>% 
  summarise(median_year = median(years))
```

## Years spent on the field

```{r}
### Histogram
descriptives %>% 
  ggplot() +
  aes(years) +
  geom_histogram() +
  labs(x = "Years spent on the field",  y = "Count") +
  scale_y_continuous(expand = c(0,0)) +
  papaja::theme_apa()
```

## Field

```{r}
### Descriptive statistics
descriptives %>% 
  group_by(field) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(N = sum(n),
         percentage = round(n / N * 100, 2))

### Barplot
descriptives %>% 
  filter(!is.na(field)) %>% 
  mutate(field = str_extract(field, "(\\w+)"),
         field = str_to_title(field),
         field = fct_relevel(field,
                             "Other",
                             "Experimental",
                             "Social",
                             "Clinical",
                             "Developmental",
                             "Applied",
                             "Neurophysiology",
                             "Methodology",
                             "Personality")) %>% 
  group_by(field) %>% 
  count() %>% 
  ggplot(.) +
  aes(x = field, y = n) +
  geom_bar(stat = "identity") +
  scale_y_continuous(expand = c(0,0)) +
  labs(x = "Field of the research teams of the respondents",
       y = "Count") + 
  papaja::theme_apa() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.line = element_line(color = "black"))
```

# Committing data management mistakes in general

# Read in data
```{r}
general_mistake_frequency <- read_tsv("Processed/ReMis_Main_Processed_General_Frequency_data.tsv")
```

# Relevel factor variable for plotting
```{r}
general_mistake_frequency <- 
  general_mistake_frequency %>% 
  mutate(general_frequency = frequency_char_to_fact(general_frequency))
```

```{r}
## Levels of the answer option to general_frequency
distinct(general_mistake_frequency, general_frequency)

## Percentage of responses to general_frequency
general_mistake_frequency %>%
  filter(!is.na(general_frequency)) %>%
  group_by(general_frequency) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(N = sum(n),
         percentage = n / N * 100)

## Barplot of the responses to general_frequency
  general_mistake_frequency %>% 
  filter(!is.na(general_frequency)) %>% 
  ggplot() +
  aes(general_frequency) +
  geom_bar() +
  scale_y_continuous(expand = c(0,0), limits = c(0, 270)) +
  labs(x = "Frequency levels",
       y = "Count") +
  coord_flip() +
  theme_apa()
```

# Analysis of the most recurring mistakes

# Read in data

```{r}
general_mistake_overview <- read_tsv("Processed/ReMis_Main_Processed_Mistake_General_data.tsv")
```

## Research data management level analyses

```{r}
### Number of responses to each investigated question
general_mistake_overview %>% 
  group_by(type, question) %>% 
  count()

### Levels of the answer option to recurring_frequency
general_mistake_overview %>% 
  filter(type == "recurring",
         question == "frequency") %>% 
  distinct(rating)

### Proportion of the frequency of the most recurring mistakes
general_mistake_overview %>%
  filter(type == "recurring",
         question == "frequency",
         !is.na(rating)) %>% 
  mutate(rating = frequency_char_to_fact(rating)) %>% 
  group_by(rating) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(N = sum(n),
         percentage = n / N * 100)

### Barplot of responses to recurring_frequency
recurring_frequency_plot <- 
  general_mistake_overview %>%
  filter(type == "recurring",
         question == "frequency",
         !is.na(rating)) %>% 
  mutate(rating = frequency_char_to_fact(rating)) %>% 
  ggplot() +
  aes(x = rating) +
  geom_bar() +
  scale_y_continuous(expand = c(0,0), limits = c(0, 250)) +
  labs(x = "Frequency levels",
       y = "Count") +
  theme_apa(box = T) +
  coord_flip()

### Proportion of the most recurring mistakes on a given seriousness level throughout research data management
general_mistake_overview %>%
  filter(type == "recurring",
         question == "serious",
         !is.na(rating)) %>% 
  mutate(rating = serious_char_to_fact(rating)) %>% 
  group_by(rating) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(N = sum(n),
         percentage = round(n / N * 100))

### Barplot of responses to recurring_serious
recurring_serious_plot <- 
  general_mistake_overview %>% 
  filter(type == "recurring",
         question == "serious",
         !is.na(rating)) %>% 
  mutate(rating = serious_char_to_fact(rating)) %>% 
  ggplot() +
  aes(rating) +
  geom_bar() +
  scale_y_continuous(expand = c(0,0), limits = c(0, 280)) +
  labs(x = "Seriousnes levels",
       y = "Count") +
  theme_classic() +
  coord_flip() +
  theme_apa(box = T)

### Median rating of all the most recurring mistakes
general_mistake_overview %>% 
  filter(type == "recurring",
         !is.na(rating)) %>% 
  mutate(rating = serious_char_to_int(rating)) %>%
  group_by(question) %>% 
  summarize(median = median(rating, na.rm = TRUE),
            max = max(rating, na.rm = TRUE),
            min = min(rating, na.rm = TRUE),
            n = n(),
            quart1 = quantile(rating, 0.25, na.rm = TRUE),
            quart3 = quantile(rating, 0.75, na.rm = TRUE),
            IQR = IQR(rating, na.rm = TRUE))
```

# Analysis of the most serious mistakes
## Research data management level analyses
```{r}
### Proportion of the most serious mistakes on a given seriousness level throughout research data management
general_mistake_overview %>%
  filter(type == "serious",
         question == "serious",
         !is.na(rating)) %>% 
  mutate(rating = serious_char_to_fact(rating)) %>%
  group_by(rating) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(N = sum(n),
         percentage = n / N * 100)

### Barplot of responses to serious_serious
serious_serious_plot <- 
  general_mistake_overview %>% 
  filter(type == "serious",
         question == "serious",
         !is.na(rating)) %>% 
  mutate(rating = serious_char_to_fact(rating)) %>%
  ggplot() +
  aes(rating) +
  geom_bar() +
  scale_y_continuous(expand = c(0,0), limits = c(0, 300)) +
  labs(x = "Seriousnes levels",
       y = "Count") +
  coord_flip() +
  theme_apa(box = T)
```

# Analysis of the mistake types for the recurring mistakes
```{r}
# Read in data
type_analysis <- read_tsv("Processed/ReMis_Main_Processed_Type_Analysis_data.tsv")

# Seriousness and frequency plot
type_analysis_plot_data <- 
  type_analysis %>% 
  filter(type == "recurring") %>% 
  spread(key = question, value = rating) %>% 
  mutate(frequency = frequency_char_to_int(frequency),
         serious = serious_char_to_int(serious)) %>%
  group_by(group_type) %>% 
  summarize(n = n(),
            mean_frequency = mean(frequency, na.rm = T),
            mean_serious = mean(serious, na.rm = T)) %>% 
  filter(n > 10)

  ggplot(data = type_analysis_plot_data) +
  aes(x = mean_frequency,
      y = mean_serious) +
  geom_text_repel(aes(label = group_type),
                  data = subset(type_analysis_plot_data, mean_serious < 2.2),
                  nudge_x = 0,
                  nudge_y = -0.15,
                  direction = "x",
                  size = 5,
                  segment.alpha = 0.6,
                  segment.size = 0.8,
                  segment.colour = "black") +
  geom_text_repel(aes(label = group_type),
                  data = subset(type_analysis_plot_data, mean_serious > 2.45 & mean_frequency < 2.4),
                  nudge_x = c(0.2, 0.1, -0.1),
                  nudge_y = c(0.2, 0.1, 0.1),
                  direction = "x",
                  size = 5,
                  segment.alpha = 0.6,
                  segment.size = 0.8,
                  segment.colour = "black") +
   geom_text_repel(aes(label = group_type),
                   data = subset(type_analysis_plot_data, mean_frequency > 2.37 & mean_serious > 2.15),
                  nudge_x = c(0.2, 0.25, 0.2),
                  nudge_y = c(0.1, 0.1, 0.1),
                  direction = "y",
                  size = 5,
                  segment.alpha = 0.6,
                  segment.size = 0.8,
                  segment.colour = "black") +
    geom_text_repel(aes(label = group_type),
                   data = subset(type_analysis_plot_data, mean_serious > 2.1 & mean_frequency < 2.1 & mean_serious < 2.65),
                  nudge_x = c(-0.1, -0.1, 0.15),
                  nudge_y = c(0.1, 0.1, -0.1),
                  direction = "y",
                  size = 5,
                  segment.alpha = 0.6,
                  segment.size = 0.8,
                  segment.colour = "black") +
    geom_text_repel(aes(label = group_type),
                   data = subset(type_analysis_plot_data, group_type %in% c("version control error", "data transfer error")),
                  nudge_x = c(0.1, 0.1),
                  nudge_y = c(0.1, 0.1),
                  direction = "y",
                  size = 5,
                  segment.alpha = 0.6,
                  segment.size = 0.8,
                  segment.colour = "black") +
      geom_point(aes(size = n), shape = 15, alpha = 1, color = "black") +
  scale_size_continuous(range = c(10, 20)) +
    geom_text(aes(label = n), color = "white") +
    scale_x_continuous(limits = c(1.8, 3), breaks = c(2, 3), label = c("Low", "Moderate")) +
    scale_y_continuous(limits = c(1.8, 3), breaks = c(2, 3), label = c("Minor", "Moderate")) +
    labs(x = "Mean Frequency Rating of the Mistake",
         y = "Mean Seriousness Rating of the Mistake") +
    theme(panel.grid = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(color = "black"),
          axis.text = element_text(color = "black", size = 15),
          axis.title = element_text(size = 20),
          legend.position = "none")
  
#ggsave("Figures/type_serious_frequency.png", width = 14.4, height = 8, plot = last_plot())
```

# Frequency and occurence of the most serious mistake types

```{r}
# Seriousness and frequency plot
type_serious_analysis <-  
  type_analysis %>% 
  filter(type == "serious") %>% 
  spread(key = question, value = rating) %>% 
  mutate(serious = serious_char_to_int(serious)) %>%
  group_by(group_type) %>% 
  summarize(n = n(),
            mean_serious = mean(serious, na.rm = T)) %>% 
  filter(n > 10)

ggplot(data = type_serious_analysis) +
  aes(x = n,
      y = mean_serious) +
  geom_point(size = 8, shape = 15, alpha = 1, color = "black") +
  geom_text_repel(aes(label = group_type),
                  force = 10,
                  max.iter = 3e3,
                  size = 5,
                  segment.alpha = 0.6,
                  segment.size = 0.8,
                  segment.colour = "black") +
  labs(x = "Number of Research Teams reported the Mistake",
       y = "Mean Seriousness Rating of the Mistake") +
  scale_y_continuous(limits = c(2, 4), breaks = c(2, 3, 4), label = c("Minor", "Moderate", "Major")) +
    theme(panel.grid = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(color = "black"),
          axis.text = element_text(color = "black", size = 15),
          axis.title = element_text(size = 20),
          legend.position = "none")

# ggsave("Figures/type_serious_serious.png", width = 14.4, height = 8, plot = last_plot())
```